---
title: "Notebook"
author: "Me"
date: "5/14/2019"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Allometry Project

> How does plant weight scale with height?

- No relationship
- Linear
- To the third power
- To the second power

## Load our data
```{r}

seeds <- read.csv("https://raw.githubusercontent.com/jmadin/himbr/master/data/seed_root_herbivores.csv", as.is=TRUE)
head(seeds)
summary(seeds)

```

## A function for standard error

```{r}

standard_error <- function(x) {
  se <- sd(x) / sqrt(length(x))
  return(se)
}

```

## Seed height/weight plotting

```{r}

plot(Weight ~ Height, data=seeds)

```

## Data transformation

```{r}

seeds$Weight_log10 <- log10(seeds$Weight)
seeds$Height_log10 <- log10(seeds$Height)

```

## Data analysis

We will run a linear regression on log-transformed variables to look for scaling coefficient. 

```{r}

mod <- lm(Weight_log10 ~ Height_log10, data=seeds)
summary(mod)
mod$coef
write.csv(mod$coef, "output/model_coefs.csv")

```

## Figure

```{r}

h <- sort(seeds$Height_log10)
pred <- predict(mod, list(Height_log10=h), interval="confidence")

pdf("figs/figure1.pdf")

plot(Weight_log10 ~ Height_log10, data=seeds, xlab="Height, log10", col="grey")
lines(h, pred[,1], col="black", lty=2)
polygon(c(h, rev(h)), c(pred[,2], rev(pred[,3])), col=rgb(0, 0, 1, 0.2), border=NA)

dev.off()

```

## Conclusions

The slope of the relationship between height and weight is `r round(mod$coef[2], 2)`.


